NFC and burnout in teachers - A replication and extension study

### 2021-09-23 Manuscript/Manuscript.Rmd
added exploratory analysis for Covid burden

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables
#install.packages("semPlot")    # plotting path models
#install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)
library(qgraph)
library(apa)                    # from the remotes package

@@

@@

  explor2_model <- '
  measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DTL =~ dtl1 + dtl2 + dtl3
    DRF =~ drf1 + drf2 + drf3
    MBI =~ mbi_ee + mbi_dp + mbi_rpe
    COVB =~ covb

  # structural model
    DTH ~ NFC
    DTL ~ NFC
    DRF ~ NFC
    COVB ~ DTH
    MBI ~ NFC + DTH + DTL + DRF + COVB'

>>>>

#install.packages("here")       # easy file referencing
#install.packages("tidyverse")  # plotting and managing data
#install.packages("lavaan")     # for structural equation modelling
#install.packages("psych")      # Cronbach's Alpha and such
#install.packages("MVN")        # Mardia's test and such
#install.packages("MBESS")      # MacDonald's Omega
#install.packages("Hmisc")      # for correlations with p-values
#install.packages("kableExtra") # for great tables (see haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
#install.packages("knitr")      # for knitting documents and tables
#install.packages("semPlot")    # plotting path models
#install.packages("remotes")    # for APA output (remotes::install_github("dgromer/apa"))
#install.packages("ppcor")      # for partial correlations

library(here)
library(tidyverse)
library(ggplot2)
library(lavaan)
library(psych)
library(MVN)
library(MBESS)
library(Hmisc)
library(kableExtra)
library(knitr)
library(GGally)                 # from ggplot2, for multi-correlation plots
library(semPlot)
library(qgraph)
library(apa)                    # from the remotes package
library(ppcor)

@@

```{r exploring_badfit, echo=FALSE, message=FALSE, warning=FALSE}

  # Use function from http://www.sthda.com/english/wiki/correlation-matrix-a-
  # quick-start-guide-to-analyze-format-and-visualize-a-correlation-matrix-
  # using-r-software#a-simple-function-to-format-the-correlation-matrix
  # accessed on September 23rd 2021

  flattenCorrMatrix <- function(cormat, pmat) {
    ut <- upper.tri(cormat)
    data.frame(
      row = rownames(cormat)[row(cormat)[ut]],
      column = rownames(cormat)[col(cormat)[ut]],
      cor  =(cormat)[ut],
      p = pmat[ut]
      )
  }

  # Compute data frame of partial correlations

  partialcorr <- flattenCorrMatrix(pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
                                                     "erq","erq_supp","erq_reap","scs","ncs",
                                                     "dth","dtl","drf","covb")], method = "spearman")$estimate,
                                  pcor(score_data[c("years","mbi","mbi_ee","mbi_dp","mbi_rpe",
                                                    "erq","erq_supp","erq_reap","scs","ncs",
                                                    "dth","dtl","drf","covb")], method = "spearman")$p.value)
  # Add easy-to-read significance column

  partialcorr$sign <- ifelse(partialcorr$p < 0.05, "sign", "ns")

@@

  explor2_model <- '
  measurement model
    NFC =~ nfc1 + nfc2 + nfc3 + nfc4
    DTH =~ dth1 + dth2 + dth3
    DRF =~ drf1 + drf2 + drf3
    MBI_EE =~ mbi_ee
    MBI_RPE =~ mbi_rpe
    SCS =~ scs
    COVB =~ covb
    YEARS =~ years

  # structural model
    COVB ~ YEARS
    SCS ~ YEARS
    NFC ~ SCS
    DTH ~ COVB + DRF
    DRF ~ SCS + NFC
    MBI_EE ~ DTH
    MBI_RPE ~ DRF'
